---
title: "Case Study"
author: "Yiqun Jin"
date: "10/14/2021"
output: html_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load the airbnb data

```{r}
data(nyc_airbnb)
```
## questions

 * How many rentals are there? Of what type? In what places?
 * Is price correlated with review scores?
 * which neighborhood is most popular? Most expensive?
 * Which neighborhood has the highest reviews?
 * Is availability related to price?
 * Is room type related to neighborhood?
 * Is length of stay related to neighborhood group (borough)?

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2)
```

Let's try to count things

```{r}
nyc_airbnb %>% 
  janitor::tabyl(neighbourhood_group, room_type)
```

Another way to count it

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

Let's look at price and room type ...

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and neighborhood

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  #summarize(mean_price = mean(price, na.rm = TRUE))
  geom_point() +
  coord_flip()
```
```{r}
nyc_airbnb %>% 
  filter(
    neighbourhood_group == "Manhattan",
    price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_boxplot() + 
  coord_flip() + 
  facet_grid(. ~ room_type)
```


Price vs location

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long,  color = price)) +
  geom_point(alpha = .5)
```

# retry leaflet map


```{r}
pal <- colorNumeric("magma", nyc_airbnb %>% pull(stars))
nyc_airbnb %>% 
  drop_na(stars) %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(stars))
```

```{r}
pal = colorNumeric("viridis", NULL)

nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  mutate(
    label = str_c("<b>Stars: ", stars, "</b><br>Price: ", price, sep = "")
  ) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(price))
```

