---
title: "Case Study"
author: "Yiqun Jin"
date: "10/14/2021"
output: html_document
---
```{r setup}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load the airbnb data

```{r}
data(nyc_airbnb)
```
## questions

How many rentals are there? Of what type? In what places?
Is price correlated with review scores?
which neighborhood is most popular? Most expensive?
Which neighborhood has the highest reviews?
Is availability related to price?
is room type related to neighborhood?
is length of stay related to neighborhood group (borough)?

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(star = review_scores_location / 2)
```

Let's try to count things

```{r}
nyc_airbnb %>% 
  janitor::tabyl(neighbourhood_group, room_type)
```

Another way to count it

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = star, y = price)) +
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and neighborhood

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  #summarize(mean_price = mean(price, na.rm = TRUE))
  geom_point() +
  coord_flip()
```
Price vs location

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long,  color = price)) +
  geom_point()
```

# retry leaflet map


```{r}
pal <- colorNumeric("magma", nyc_airbnb %>% pull(star))
nyc_airbnb %>% 
  drop_na(star) %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(star))
```

```{r}
pal = colorNumeric("viridis", NULL)
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  mutate(
    lables = str_c("<b>Price:", price, "</b><br>Stars:", star)
  ) %>% 
  leaflet() %>% 
  #addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  #addMarkers(~lat, ~long) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(price))
```

